---
title: "R Package: bccdc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R Package: bccdc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bccdc)
```

This document contains detailed documentation and examples for the functions 
which can be found in the bccdc package. In general, these function can be used 
for bccdc vaccine coverage analysis sticking to the dataset that is in the same 
format with the 2022's version. 

The package includes the following 5 functions:

* var_assign()
* atg_in()
* atg_ex()
* trans_cvg()
* output_file()

## var_assign()
The function `var_assign()` ...For example, given the following 
grade_name:
```{r var-assign-input}
#...
```

```{r var-assign-example}
#var_assign(...)
```

## atg_in()
The function `atg_in()` ...For example, given the following 
grade_name:
```{r atg-in-input}
#...
```

```{r atg-in-example}
#var_assign(...)
```

## atg_ex()
The function `atg_ex()` ...For example, given the following 
grade_name:
```{r atg-ex-input}
#...
```

```{r atg-ex-example}
#atg_ex(...)
```

## trans_cvg()
The function `trans_cvg()` ...For example, given the following 
grade_name:
```{r trans-cvg-input}
#...
```

```{r trans-cvg-example}
#trans_cvg(...)
```

## output_file()
The function `output_file()` ...For example, given the following 
grade_name:
```{r output-file-input}
#...
```

```{r output-file-example}
#output_file(...)
```
